draftFiguresPaper

### 2025-12-08 draftFiguresPaper.Rmd
reorganizing

# 2) get total papers by country
papers_by_country <- datasetClassificationCountries_long_clean %>%
  group_by(iso3, .drop = F) %>% 
  count(iso3, name = "n_papers") %>%
  arrange(desc(n_papers))

>>>>

df_cat_long <- datasetClassificationCountries_long_clean %>%
  # keep only “paper belongs to this category”
  filter(sum(Perceptions, Priority, Policy, Health, Behavior) >= 1,
         None != 1)

# 2) get total papers by country
papers_by_country <- df_cat_long %>%
  group_by(iso3, .drop = F) %>% 
  count(iso3, name = "n_papers") %>%
  arrange(desc(n_papers))
